<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-03-31 figures_01312022.Rmd
Rmarkdown figure edits

data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")

@@

  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "fk_extraction_document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

@@

write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)

write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
```

@@

@@

@@

### save data
save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")

@@

### load all of this wonderful data
load("figures_rdata/pk_output_1comp_12212021.Rdata")
load("figures_rdata/pk_output_2comp_12212021.Rdata")
load("figures_rdata/raw_1comp_12212021.Rdata")
load("figures_rdata/raw_2comp_12212021.Rdata")
load("figures_rdata/cp_df_12212021.Rdata")
load("figures_rdata/cvt_variability_df_12212021.Rdata")
load("figures_rdata/pk_lombardo_02072022.Rdata")
```

@@

### 1 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
                      data.set = as.data.table(raw_1comp_12212021),
                      model = "1compartment")

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_02102022),
                      data.set = as.data.table(raw_2comp_02102022),
                      model = "2compartment")

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data1 <- dplyr::select(raw_1comp_12212021, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs"))

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_02102022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_02102022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

### make both data.frames have the same column names so they are rbind-able
cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
cp_df_2 <- cp_df_2[, intersect(colnames(cp_df_1), colnames(cp_df_2))]

@@

@@

cp_df_12212021 <- cp_df

save(cp_df_12212021, file = "figures_rdata/cp_df_12212021.Rdata")
```

@@

data <- cp_df_12212021

@@

data <- as.data.table(raw_1comp_12212021)

@@

  ### only use data with replicate timepoints
  data <- data[ ave(1:nrow(data), data$Time, fun = length) > 1 , ]

@@

### combine data.tables back into one large data.set
cvt_variability_df_12212021 <- do.call(rbind, data.list)

save(cvt_variability_df_12212021, file = "figures_rdata/cvt_variability_df_12212021.Rdata")
```

@@

data <- cvt_variability_df_12212021

@@

p <- ggplot(data, aes(x = conc_norm)) +
  geom_histogram() +
  xlim(c(0, 4)) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  theme_bw() +
  labs(x = "Normalized concentration",
       y = "Number of observations")
p
```

@@

pk_data <- cp_df_12212021

cvt_data <- cvt_variability_df_12212021

@@

cvt_data <- dplyr::select(cvt_data, -c("X",
                                       "kelim", 
                                       "Vdist", 
                                       "Fgutabs", 
                                       "kgutabs"))

@@

### put data back together
full_data <- rbind(full_data_1, full_data_2)

@@

@@

@@

full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_2_green <- full_data_2 %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))

@@

@@

p <- ggplot(data = full_data,
            mapping = aes(x = conc_norm, y = cp_norm)) +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  geom_bin2d(bins = 100) +
  scale_fill_distiller(palette = "Blues") +
  geom_vline(xintercept = c(0.5, 2),
             linetype = "dashed") +
  geom_hline(yintercept = c(0.5, 2),
             linetype = "dashed") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Data Variability",
       y = "Model Error") +
  facet_wrap(. ~ type)

@@

data1 <- pk_output_1comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

data2 <- pk_output_2comp_02102022 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

@@

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model) +
  geom_vline(xintercept = 2.22e-06)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

@@

data <- raw_1comp_12212021

@@

```{r make_joint_sigma_plot}

@@

data1 <- as.data.table(pk_output_1comp_12212021 %>%
                         filter(param.value.type == "Fitted geometric mean"))

data2 <- as.data.table(pk_output_2comp_02102022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

raw_data1 <- raw_1comp_12212021

@@

pk_data1 <- pk_output_1comp_12212021 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

raw_data2 <- raw_2comp_02102022

pk_data2 <- pk_output_2comp_02102022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

```{r, make_model_params_table}

@@

pk_data1 <- pk_output_1comp_12212021

pk_data2 <- pk_output_2comp_02102022

@@

# write.csv(fittable, file = "inst/ext/model_params_table.csv", row.names = FALSE)

@@

pk_data1 <- as.data.table(pk_output_1comp_12212021)
pk_data2 <- as.data.table(pk_output_2comp_02102022)

@@

# write.csv(pk_all, file = "inst/ext/no_fit_table_01212022.csv", row.names = FALSE)
```

@@

pk_data1 <- pk_output_1comp_12212021

pk_data2 <- pk_output_2comp_02102022

pk_data_flat <- pk_output_flat_02102022 %>%
  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")

@@

pk_data1 <- pk_output_1comp_12212021

>>>>

data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")

@@

  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

@@

# write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
# write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
# 
# write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
# write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
```

@@

pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")

@@

raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")

@@

### save data
# save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
# save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
# save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
# save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
# save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
# save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")

save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")

save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")

@@

### load all of this wonderful data
load("figures_rdata/pk_output_1comp_12212021.Rdata")
load("figures_rdata/pk_output_2comp_12212021.Rdata")
load("figures_rdata/raw_1comp_12212021.Rdata")
load("figures_rdata/raw_2comp_12212021.Rdata")
load("figures_rdata/cp_df_12212021.Rdata")
load("figures_rdata/cvt_variability_df_12212021.Rdata")

load("figures_rdata/pk_output_1comp_03012022.Rdata")
load("figures_rdata/pk_output_2comp_03012022.Rdata")
load("figures_rdata/pk_output_flat_03012022.Rdata")
load("figures_rdata/raw_1comp_03012022.Rdata")
load("figures_rdata/raw_2comp_03012022.Rdata")
load("figures_rdata/raw_flat_03012022.Rdata")
load("figures_rdata/cp_df_03012022.Rdata")
load("figures_rdata/cvt_variability_df_03012022.Rdata")

load("figures_rdata/cp_df_03302022.Rdata")

load("figures_rdata/pk_lombardo_02072022.Rdata")
```

@@

### 1 compartment

pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
  filter(Compound == "tamoxifen") %>%
  filter(Data.Analyzed != "Joint Analysis")

raw_1comp_03012022 <- raw_1comp_03012022 %>%
  filter(Compound == "tamoxifen")

junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
                      data.set = as.data.table(raw_1comp_12212021),
                      model = "1compartment")

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_03012022),
                      data.set = as.data.table(raw_2comp_03012022),
                      model = "2compartment")

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data1 <- dplyr::select(raw_1comp_03012022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs"))

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_03012022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

###########
### this is flat data
###########

pk_data_flat <- pk_output_flat_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data_flat <- dplyr::select(raw_flat_03012022, -c("A"))

raw_data_flat$Reference <- as.character(raw_data_flat$Reference)

full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
full_data_flat <- full_data_flat %>% filter(AIC != Inf)
split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
                                            full_data_flat$Reference,
                                            full_data_flat$CAS),
                       drop = TRUE)

### function that finds cp
find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
                                                                                              params = full_data_flat[1,],
                                                                                              dose = Dose,
                                                                                              iv.dose = iv))}
cp_df_flat <- lapply(split_df_flat, find_cp_flat)

cp_df_flat <- do.call(rbind, cp_df_flat)

cp_df_flat$cp_norm <- cp_df_flat$cp / cp_df_flat$Value
cp_df_flat$type <- "Flat"

### make all data.frames have the same column names so they are rbind-able
cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
cp_df_2 <- cp_df_2[, intersect(colnames(cp_df_1), colnames(cp_df_2))]

@@

cp_df <- cp_df[, intersect(colnames(cp_df_flat), colnames(cp_df))]
cp_df_flat <- cp_df_flat[, intersect(colnames(cp_df), colnames(cp_df))]

cp_df <- rbind(cp_df, cp_df_flat)

@@

cp_df_03302022 <- cp_df

save(cp_df_03302022, file = "figures_rdata/cp_df_03302022.Rdata")
```

@@

# data <- cp_df_12212021
data <- cp_df_03012022

@@

data <- as.data.table(raw_1comp_03012022)

@@

  ### only use data with replicate timepoints
  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]

@@

### combine data.tables back into one large data.set
cvt_variability_df_03012022 <- do.call(rbind, data.list)

save(cvt_variability_df_03012022, file = "figures_rdata/cvt_variability_df_03012022.Rdata")
```

@@

data <- cvt_variability_df_03012022
# data <- cvt_variability_df_12212021

@@

p <- ggplot(data, aes(x = conc_norm)) +
  geom_histogram(binwidth = 0.25) +
  xlim(c(-0.5, 4)) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  theme_bw() +
  labs(x = "Normalized concentration",
       y = "Number of observations")
p
```

@@

# pk_data <- cp_df_03012022
pk_data <- cp_df_03302022

cvt_data <- cvt_variability_df_03012022

@@

cvt_data <- dplyr::select(cvt_data, -c("kelim", 
                                       "Vdist", 
                                       "Fgutabs", 
                                       "kgutabs"))

@@

cvt_data$type <- "Flat"
full_data_flat <- left_join(cvt_data, model_split$`flat`)

### put data back together
full_data <- rbind(full_data_1, full_data_2, full_data_flat)

full_data <- full_data %>%
  filter(cp != 0)

full_data$AIC <- round(full_data$AIC, digits = 4)

full_data <- full_data %>%
  distinct(Compound, Reference, model, conc_norm, AIC, cp_norm)

### 
full_data <- full_data %>%
  pivot_wider(names_from = model,
              values_from = c(AIC, cp_norm)) %>%
  unchop(everything())

full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
                                                      AIC_1compartment < AIC_flat ~ "1compartment",
                                                    AIC_2compartment < AIC_1compartment &
                                                      AIC_2compartment < AIC_flat ~ "2compartment",
                                                    AIC_flat < AIC_1compartment &
                                                      AIC_flat < AIC_2compartment ~ "flat",

                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
                                                      is.na(AIC_flat) ~ "1compartment",
                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
                                                      is.na(AIC_flat) ~ "2compartment",
                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
                                                      is.na(AIC_2compartment) ~ "flat",

                                                    is.na(AIC_1compartment) &
                                                      AIC_flat < AIC_2compartment ~ "flat",
                                                    is.na(AIC_1compartment) &
                                                      AIC_2compartment < AIC_flat ~ "2compartment",
                                                    is.na(AIC_2compartment) &
                                                      AIC_flat < AIC_1compartment ~ "flat",
                                                    is.na(AIC_2compartment) &
                                                      AIC_1compartment < AIC_flat ~ "1compartment",
                                                    is.na(AIC_flat) &
                                                      AIC_1compartment < AIC_2compartment ~"1compartment",
                                                    is.na(AIC_flat) &
                                                      AIC_2compartment <AIC_1compartment ~"2compartment"))

full_data <- full_data %>%
  mutate(cp_norm = case_when(model == "1compartment" ~ cp_norm_1compartment,
                             model == "2compartment" ~ cp_norm_2compartment,
                             model == "flat" ~ cp_norm_flat))

# full_data <- full_data %>%
#   mutate(cp_norm = case_when(model == "1comparment" ~ cp_norm_1compartment,
#                              model == "2compartment" ~ cp_norm_2compartment))

# full_data$cp_norm[full_data$model == "2compartment"] <- full_data$cp_norm_2compartment
# full_data$cp_norm[full_data$model == "1compartment"] <- full_data$cp_norm_1compartment

# full_data <- full_data %>%
# mutate(across(everything(), ~ifelse(. == "", NA, as.character(.))))

# filter(Compound != "triclosan")
# filter(Compound != "tamoxifen")

@@

split_full_data <- split(full_data, full_data$model)

full_data_1 <- split_full_data$`1compartment`

@@

full_data_2 <- split_full_data$`2compartment`

@@

full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_2_green <- full_data_2_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))

@@

full_data_flat <- split_full_data$`flat`

### Find number of points in each plot panel for 2-compartment
full_data_flat_center <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_flat_center <- full_data_flat_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_flat_center <- nrow(full_data_flat_center) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))

full_data_flat_green <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_flat_green <- full_data_flat_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_flat_green <- nrow(full_data_flat_green) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))

full_data_flat_gray <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_flat_gray <- full_data_flat_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_flat_gray <- nrow(full_data_flat_gray) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))

full_data_flat_tan <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_flat_tan <- full_data_flat_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_flat_tan <- nrow(full_data_flat_tan) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))

@@

p <- ggplot(data = full_data,
            mapping = aes(x = conc_norm, y = cp_norm)) +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0.5, ymax = 2.0, alpha = 0.5, fill = "black") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  geom_bin2d(bins = 100) +
  scale_fill_distiller(palette = "Blues") +
  geom_vline(xintercept = c(0.5, 2),
             linetype = "dashed") +
  geom_hline(yintercept = c(0.5, 2),
             linetype = "dashed") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Data Variability",
       y = "Model Performance") +
  facet_wrap(. ~ model)

@@

data1 <- pk_output_1comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

data2 <- pk_output_2comp_03012022 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

@@

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model) +
  geom_vline(xintercept = 0.001476315)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

@@

data <- raw_1comp_03012022

@@

```{r make_joint_sigma_plot, eval = FALSE}

@@

data1 <- as.data.table(pk_output_1comp_03012022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

data2 <- as.data.table(pk_output_2comp_03012022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

raw_data1 <- raw_1comp_03012022

@@

pk_data1 <- pk_output_1comp_03012022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

raw_data2 <- raw_2comp_03012022

pk_data2 <- pk_output_2comp_03012022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

```{r, make_model_params_table, eval = FALSE}

@@

pk_data1 <- pk_output_1comp_03012022 
pk_data1 <- pk_output_1comp_12212021

pk_data2 <- pk_output_2comp_03012022
pk_data2 <- pk_output_2comp_12212021

@@

write.csv(fittable, file = "inst/ext/model_params_table_03012022.csv", row.names = FALSE)

@@

pk_data1 <- as.data.table(pk_output_1comp_03012022)
pk_data2 <- as.data.table(pk_output_2comp_03012022)

@@

# write.csv(pk_all, file = "inst/ext/no_fit_table_03012022.csv", row.names = FALSE)
```

@@

pk_data1 <- pk_output_1comp_03012022

pk_data2 <- pk_output_2comp_03012022

pk_data_flat <- pk_output_flat_03012022 %>%
  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")

@@

pk_data1 <- pk_output_1comp_03012022
